---
title: "yearly_publication_PubMed"
# author: "Emtiaz"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(scales)
library(zoo)
library(ggpubr)
library(latex2exp)
library(gg.gap)
```

# NIMH funding
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_NIMH = read.csv("Data/NIMH_emoVSnonemo.csv",stringsAsFactors = FALSE)
df_NIMH
```

#### select specific columns; convert data types
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_NIMH = df_NIMH %>% select(year, yFUND_emo_2018, fundPercentage)

df_NIMH$year = as.integer(df_NIMH$year)
df_NIMH$yFUND_emo_2018 = as.double(df_NIMH$yFUND_emo_2018)
df_NIMH$fundPercentage = as.double(df_NIMH$fundPercentage)

df_NIMH
```
#### Filter NIMH year from 1985-2018;
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_NIMH = df_NIMH %>% filter(year >= 1985 & year <= 2018)
df_NIMH
```
#### Draw bar plot

```{r echo=FALSE, warning=FALSE, message=FALSE}

g_fund_bar = ggplot(df_NIMH, aes(x=year, y=fundPercentage)) +
  geom_bar(stat = "identity", fill="darkgray", alpha= 0.7) +
  coord_cartesian(xlim = c(1984,2018)) +
  scale_x_continuous(breaks = seq(1985,2018,by=3), limits = c(1984,2019)) +
  scale_y_continuous(breaks = seq(0,15, by = 3), limits = c(0,15), labels=function(x) paste0(x," %")) +
  theme_bw()+
  theme(panel.grid.major = element_blank(),
        axis.text=element_text(size=17, face="bold"),
        axis.title=element_text(size=18,face="bold"),
        legend.position = "none",
        axis.title.y = element_text(margin=margin(t=0,r=10,b=0,l=0)),
        axis.title.x = element_text(margin=margin(t=10,r=0,b=0,l=0)),
        plot.margin = margin(t=0.8, l=1.5, r=1, b=0.3, unit = "cm"),
        plot.title = element_text(hjust = 0.5, size = 24, face="bold"))+
  labs(x="", y="NIMH budget share", title = "Affective research funding")


g_fund_bar
```

## Yearly publication


### Read all files and set the data types
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_emotion_pubmed = read.csv("Data/timeline_Emotions.csv",stringsAsFactors = FALSE)
df_behavior_pubmed = read.csv("Data/timeline_behavior.csv",stringsAsFactors = FALSE)

df_emotion_pubmed$year = as.integer(df_emotion_pubmed$year)
df_emotion_pubmed$count = as.integer(df_emotion_pubmed$count)
df_emotion_pubmed

df_behavior_pubmed$year = as.integer(df_behavior_pubmed$year)
df_behavior_pubmed$count = as.integer(df_behavior_pubmed$count)
df_behavior_pubmed

```

### Filter year from 1980 to 2018
```{r echo=FALSE, warning=FALSE, message=FALSE}

df_emotion_pubmed = df_emotion_pubmed %>% filter(year >= 1980 & year<=2018)
df_emotion_pubmed

df_behavior_pubmed = df_behavior_pubmed %>% filter(year >= 1980 & year<=2018)
df_behavior_pubmed



```

### Rename column names and join them together
```{r echo=FALSE, warning=FALSE, message=FALSE}
colnames(df_emotion_pubmed) <- c('year', 'emotion_count')

df_yearly = df_emotion_pubmed %>% merge(df_behavior_pubmed, by ='year')
df_yearly
```

### Calculate the percentages
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_yearly = df_yearly %>% mutate(emoPercent = emotion_count * 100 / count)
df_yearly
```
# Draw bar plot

```{r echo=FALSE, warning=FALSE, message=FALSE}

g_pub_bar = ggplot(df_yearly, aes(x=year, y=emoPercent)) +
  geom_bar(stat = "identity", fill="black", alpha= 0.8) +
  coord_cartesian(xlim = c(1979,2019)) +
  scale_x_continuous(breaks = seq(1980,2018,by=4), limits = c(1979,2019))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),
        axis.text=element_text(size=17, face="bold"),
        axis.title=element_text(size=18,face="bold"),
        legend.position = "none",
        axis.title.y = element_text(margin=margin(t=0,r=10,b=0,l=0)),
        axis.title.x = element_text(margin=margin(t=10,r=0,b=0,l=0)),
        plot.margin = margin(t=0.5, l=1.5, r=1, b=0.5, unit = "cm"),
        plot.title = element_text(hjust = 0.5, size = 24, face="bold"))+
  labs(x="", y="Publication volume share", title = "Affective content in 'Behaviour' research")+
  scale_y_continuous(breaks = seq(0,10, by = 2), limits = c(0,10), labels=function(x) paste0(x," %"))

g_pub_bar
```

### generate combined plots
```{r echo=FALSE, warning=FALSE, message=FALSE}

g_fund_pub_bar <- ggarrange(g_fund_bar, g_pub_bar,
                     ncol = 1, nrow = 2,
                     labels = c("b", "c"),
                     font.label=list(color="black",size=30, face = "bold")) + border(color = "black", size = 2, linetype = NULL)



g_fund_pub_bar

```



# Attention, Decision, Memory, Perception publication details

### Read all files and set the data types
```{r echo=FALSE, warning=FALSE, message=FALSE}

df_memory_emotion = read.csv("Data/timeline_memory_emotion.csv",stringsAsFactors = FALSE)
df_memory = read.csv("Data/timeline_memory.csv",stringsAsFactors = FALSE)

df_attention_emotion = read.csv("Data/timeline_attention_emotion.csv",stringsAsFactors = FALSE)
df_attention = read.csv("Data/timeline_attention.csv",stringsAsFactors = FALSE)

df_perception_emotion = read.csv("Data/timeline_perception_emotion.csv",stringsAsFactors = FALSE)
df_perception = read.csv("Data/timeline_perception.csv",stringsAsFactors = FALSE)

df_decision_emotion = read.csv("Data/timeline_decision_emotion.csv",stringsAsFactors = FALSE)
df_decision = read.csv("Data/timeline_decision.csv",stringsAsFactors = FALSE)


df_memory_emotion$year = as.integer(df_memory_emotion$year)
df_memory_emotion$count = as.integer(df_memory_emotion$count)
df_memory$year = as.integer(df_memory$year)
df_memory$count = as.integer(df_memory$count)

df_attention_emotion$year = as.integer(df_attention_emotion$year)
df_attention_emotion$count = as.integer(df_attention_emotion$count)
df_attention$year = as.integer(df_attention$year)
df_attention$count = as.integer(df_attention$count)

df_perception_emotion$year = as.integer(df_perception_emotion$year)
df_perception_emotion$count = as.integer(df_perception_emotion$count)
df_perception$year = as.integer(df_perception$year)
df_perception$count = as.integer(df_perception$count)

df_decision_emotion$year = as.integer(df_decision_emotion$year)
df_decision_emotion$count = as.integer(df_decision_emotion$count)
df_decision$year = as.integer(df_decision$year)
df_decision$count = as.integer(df_decision$count)


df_memory_emotion
df_memory
df_attention_emotion
df_attention
df_perception_emotion
df_perception
df_decision_emotion
df_decision



```


### Filter year from 1980 to 2018
```{r echo=FALSE, warning=FALSE, message=FALSE}

df_memory_emotion = df_memory_emotion %>% filter(year >= 1980 & year<=2018)
df_memory_emotion
df_memory = df_memory %>% filter(year >= 1980 & year<=2018)
df_memory

df_attention_emotion = df_attention_emotion %>% filter(year >= 1980 & year<=2018)
df_attention_emotion
df_attention = df_attention %>% filter(year >= 1980 & year<=2018)
df_attention

df_perception_emotion = df_perception_emotion %>% filter(year >= 1980 & year<=2018)
df_perception_emotion
df_perception = df_perception %>% filter(year >= 1980 & year<=2018)
df_perception

df_decision_emotion = df_decision_emotion %>% filter(year >= 1980 & year<=2018)
df_decision_emotion
df_decision = df_decision %>% filter(year >= 1980 & year<=2018)
df_decision

```

### Rename column names and join them together
```{r echo=FALSE, warning=FALSE, message=FALSE}

colnames(df_memory_emotion) <- c('year', 'emotion_count')
emotion_memory_yearly = df_memory_emotion %>% merge(df_memory, by ='year')
emotion_memory_yearly

colnames(df_attention_emotion) <- c('year', 'emotion_count')
emotion_attention_yearly = df_attention_emotion %>% merge(df_attention, by ='year')
emotion_attention_yearly

colnames(df_perception_emotion) <- c('year', 'emotion_count')
emotion_perception_yearly = df_perception_emotion %>% merge(df_perception, by ='year')
emotion_perception_yearly

colnames(df_decision_emotion) <- c('year', 'emotion_count')
emotion_decision_yearly = df_decision_emotion %>% merge(df_decision, by ='year')
emotion_decision_yearly

```

### Calculate the percentages
```{r echo=FALSE, warning=FALSE, message=FALSE}
emotion_memory_yearly  = emotion_memory_yearly  %>% mutate(emoPercent = emotion_count * 100 / count)
emotion_memory_yearly

emotion_attention_yearly  = emotion_attention_yearly  %>% mutate(emoPercent = emotion_count * 100 / count)
emotion_attention_yearly

emotion_perception_yearly  = emotion_perception_yearly  %>% mutate(emoPercent = emotion_count * 100 / count)
emotion_perception_yearly

emotion_decision_yearly  = emotion_decision_yearly  %>% mutate(emoPercent = emotion_count * 100 / count)
emotion_decision_yearly


```

#### Draw bar Plot
```{r echo=FALSE, warning=FALSE, message=FALSE}




g_emo_mem = ggplot(emotion_memory_yearly, aes(x=year, y=emoPercent)) +
  geom_bar(stat = "identity", fill="cyan2", alpha= 0.8) +
  coord_cartesian(xlim = c(1979,2019)) +
  scale_x_continuous(breaks = seq(1980,2018,by=4), limits = c(1979,2019))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),
        axis.text=element_text(size=17, face="bold"),
        axis.title=element_text(size=18,face="bold"),
        legend.position = "none",
        axis.title.y = element_text(margin=margin(t=0,r=10,b=0,l=0)),
        axis.title.x = element_text(margin=margin(t=10,r=0,b=0,l=0)),
        plot.margin = margin(t=0.5, l=1.5, r=1, b=0.2, unit = "cm"),
        plot.title = element_text(hjust = 0.5, size = 24, face="bold"))+
  labs(x="", y=expression(bold("Publication volume share")), title = "Affective content in 'Memory' research")+
  scale_y_continuous(breaks = seq(0,12, by = 4), limits = c(0,12), labels=function(x) paste0(x," %"))



g_emo_att = ggplot(emotion_attention_yearly, aes(x=year, y=emoPercent)) +
  geom_bar(stat = "identity", fill="palevioletred1", alpha= 0.8) +
  coord_cartesian(xlim = c(1979,2019)) +
  scale_x_continuous(breaks = seq(1980,2018,by=4), limits = c(1979,2019))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),
        axis.text=element_text(size=17, face="bold"),
        axis.title=element_text(size=18,face="bold"),
        legend.position = "none",
        axis.title.y = element_text(margin=margin(t=0,r=10,b=0,l=0)),
        axis.title.x = element_text(margin=margin(t=10,r=0,b=0,l=0)),
        plot.margin = margin(t=0.5, l=1.5, r=1, b=0.2, unit = "cm"),
        plot.title = element_text(hjust = 0.5, size = 24, face="bold"))+
  labs(x="", y=expression(bold("Publication volume share")), title = "Affective content in 'Attention' research")+
  scale_y_continuous(breaks = seq(0,12, by = 4), limits = c(0,12), labels=function(x) paste0(x," %"))



g_emo_per = ggplot(emotion_perception_yearly, aes(x=year, y=emoPercent)) +
  geom_bar(stat = "identity", fill="orange", alpha= 0.8) +
  coord_cartesian(xlim = c(1979,2019)) +
  scale_x_continuous(breaks = seq(1980,2018,by=4), limits = c(1979,2019))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),
        axis.text=element_text(size=17, face="bold"),
        axis.title=element_text(size=18,face="bold"),
        legend.position = "none",
        axis.title.y = element_text(margin=margin(t=0,r=10,b=0,l=0)),
        axis.title.x = element_text(margin=margin(t=10,r=0,b=0,l=0)),
        plot.margin = margin(t=0.4, l=1.5, r=1, b=0.3, unit = "cm"),
        plot.title = element_text(hjust = 0.5, size = 24, face="bold"))+
  labs(x="", y=expression(bold("Publication volume share")), title = "Affective content in 'Perception' research")+
  scale_y_continuous(breaks = seq(0,7, by = 2), limits = c(0,7), labels=function(x) paste0("  ", x," %"))



g_emo_dec = ggplot(emotion_decision_yearly, aes(x=year, y=emoPercent)) +
  geom_bar(stat = "identity", fill="green", alpha= 0.8) +
  coord_cartesian(xlim = c(1979,2019)) +
  scale_x_continuous(breaks = seq(1980,2018,by=4), limits = c(1979,2019))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),
        axis.text=element_text(size=17, face="bold"),
        axis.title=element_text(size=18,face="bold"),
        legend.position = "none",
        axis.title.y = element_text(margin=margin(t=0,r=10,b=0,l=0)),
        axis.title.x = element_text(margin=margin(t=10,r=0,b=0,l=0)),
        plot.margin = margin(t=0.4, l=1.5, r=1, b=0.3, unit = "cm"),
        plot.title = element_text(hjust = 0.5, size = 24, face="bold"))+
  labs(x="", y=expression(bold("Publication volume share")), title = "Affective content in 'Decision-making' research")+
  scale_y_continuous(breaks = seq(0,7, by = 2), limits = c(0,7), labels=function(x) paste0("  ", x," %"))

g_emo_mem
g_emo_att
g_emo_per
g_emo_dec

```

### combine  plots
```{r echo=FALSE, warning=FALSE, message=FALSE}

g_mem_att_dec_per <- ggarrange(g_emo_mem, g_emo_att, g_emo_per, g_emo_dec,
                     labels = c("d", "e", "f", "g"),
                     ncol = 2, nrow = 2,
                     font.label=list(color="black",size=30, face = "bold"))  + border(color = "black", size = 2, linetype = NULL)



g_mem_att_dec_per
```



### combine  plots full
```{r echo=FALSE, warning=FALSE, message=FALSE}

# g_full <- ggarrange(g_top_part, g_mem_att_dec_per,
#                      labels = c("", "c"),
#                      ncol = 1, nrow = 2,
#                      font.label = list(size=19))
# 
# 
# g_full
# ggsave(paste0("Plots/full.png"), g_full, height = 17, width = 26)

library(ggpubr)
library(png)
library(jpeg)

img1 <- readJPEG("Plots/conceptual.jpg")
# img1 <- readPNG("Plots/conceptual.png")

im_A <- ggplot() + 
    background_image(img1) + theme_bw() + 
    # This ensures that the image leaves some space at the edges
    theme(plot.margin = margin(t=1.5, l=1.5, r=1, b=1, unit = "cm"), axis.line = element_blank(),
          panel.border = element_blank(), panel.grid = element_blank(), panel.ontop = element_blank()) 
# + border(color = "black", size = 2, linetype = NULL)


g_f = ggarrange(ggarrange(im_A, g_fund_pub_bar, labels = c("a", ""), ncol=2, font.label=list(color="black",size=30, face = "bold")),
                g_mem_att_dec_per, 
                labels = c("", ""), 
                font.label=list(color="black",size=30, face = "bold"),
                nrow = 2)
g_f
ggsave(paste0("Plots/full_figure_affective_research.png"), g_f, height = 17, width = 26)
ggsave(paste0("Plots/full_figure_affective_research.jpg"), g_f, height = 17, width = 26)
ggsave(paste0("Plots/full_figure_affective_research.pdf"), g_f, height = 17, width = 26)
```

### combine  plots full
```{r echo=FALSE, warning=FALSE, message=FALSE}
# 
# library(ggpubr)
# library(png)
# library(jpeg)
# 
# # img1 <- readJPEG("Plots/conceptual.jpg")
# img1 <- readPNG("Plots/conceptual_border.png")
# 
# im_A <- ggplot() + 
#     background_image(img1) +
#     # This ensures that the image leaves some space at the edges
#     theme(plot.margin = margin(t=1.5, l=1.5, r=1, b=1, unit = "cm")) + border(color = "black", size = 2, linetype = NULL)
# 
# 
# g_f = ggarrange(ggarrange(im_A, g_fund_pub_bar, labels = c("a", ""), ncol=2, font.label=list(color="black",size=30, face = "bold")),
#                 g_mem_att_dec_per, 
#                 labels = c("", ""), 
#                 font.label=list(color="black",size=30, face = "bold"),
#                 nrow = 2)
# g_f
# ggsave(paste0("Plots/full_figure_affective_research_v2.png"), g_f, height = 17, width = 26)
```

